full title

### 2020-10-29 paper/pldi21/intro.tex
Added the implementation section.
Revising motivation.

We present a more flexible and fine-grained method to combine two analyses to
maximize the benefits.
Our idea enables abstract interpretation to use the dynamic analysis on demand
to speed up the analysis while preserving soundness, so we call that adding
dynamic shortcuts.
We extend a dynamic analysis to work as long as possible despite of the presence
of abstract values by laziness.
The analysis goes on the concrete engine as much as possible until it meets
operations with non-deterministic values by abstract values or analysis
sensitivity that the concrete engine cannot handle.
When the dynamic shortcut meets non-determinism, the analysis switches to
the traditional static analysis and uses its abstract semantics to handle that.
As soon as analysis sensitivity is deterministic, it continues to take the
dynamic shortcut again.

@@

In summary, the contributions of this paper are as follows.
\begin{itemize}
\item We formally describe the high-level idea of adding dynamic shortcuts, a
  technique for combining static and dynamic analyses into fine-grained level on
  the general abstract interpretation framework.
\item We actualize our method by extending the existing JavaScript static analyzer SAFE 2.0.
\item We empirically evaluate our technique using the implementation.
  We find that using dynamic shortcut significantly increased performance for
  benchmark programs enhanced with abstracted input that existing combined
  analysis designs cannot handle.
\end{itemize}
The remainder of this paper is organized as follows.
In Section~\ref{sec:motivation}, we explain more details about limitations of
existing techniques and our solution with the real-world JavaScript programs.
Section~\ref{sec:formal} formalizes adding dynamic shortucts on abstract
interpretation.
We explain JavaScript related features formalized with core language of
JavaScript in Section~\ref{sec:javascript}.
We explain key implementation techniques like the synchronizetion of two analyses.
We evaluate our idea using real-world benchmarks in Section~\ref{sec:eval}.
We organize related work in Section~\ref{sec:related}, and we conclude in Section~\ref{sec:conclusion}.

>>>>

We present a more flexible and fine-grained method to combine two analyses to
maximize the benefits.
Our idea enables abstract interpretation to use the dynamic analysis on demand
to speed up the analysis while preserving soundness, so we call that adding
dynamic shortcuts.
We use a linear symbolic execution as dynamic analysis to analyze program on the
concrete engine as long as possible despite of the presence of abstract values.
The analysis goes on the concrete engine as much as possible until it meets
operations with non-deterministic values by abstract values or analysis
sensitivity that the concrete engine cannot handle.
When the dynamic shortcut meets non-determinism, the analysis switches to
the traditional static analysis and uses its abstract semantics to handle that.
As soon as analysis sensitivity is deterministic, it continues to take the
dynamic shortcut again.

@@

In summary, the contributions of this paper are as follows.
\begin{itemize}
\item We formally describe the high-level idea of adding dynamic shortcuts, a
  technique for combining static and dynamic analyses into fine-grained level on
  the general abstract interpretation framework.
\item We actualize our method by extending the existing JavaScript static analyzer SAFE 2.0.
\item We empirically evaluate our technique using the implementation.
  We find that using dynamic shortcut significantly increased performance for
  benchmark programs enhanced with abstracted input that existing combined
  analysis designs cannot handle.
\end{itemize}
The remainder of this paper is organized as follows.
In Section~\ref{sec:motivation}, we explain more details about limitations of
existing techniques and our solution with the real-world JavaScript programs.
Section~\ref{sec:formal} formalizes adding dynamic shortucts on abstract
interpretation.
We explain JavaScript related features formalized with core language of
JavaScript in Section~\ref{sec:javascript}.
Section~\ref{sec:implementation} describes key implementation techniques like the synchronizetion of two analyses.
We evaluate our idea using real-world benchmarks in Section~\ref{sec:eval}.
We organize related work in Section~\ref{sec:related}, and we conclude in Section~\ref{sec:conclusion}.

### 2020-10-29 paper/pldi21/motivation.tex
Revising motivation.

A low degree of context sensitivity tends to face spurious callee explosion
during analyzing \jscode{concat} function.
The analysis is not supposed to lose precision for the loop in line 7-8.
Moreover, \jscode{baseFlatten} has a recursive call in a loop that is a
traditional challenge for static analysis.

We excerpt two functions \jscode{changeCountry} in Figure~\ref{fig:changeCountry}
and \jscode{getData} in Figure~\ref{fig:getData} from the \code{zoom.us}~\cite{zoom}
site.
The website \code{zoom.us} is ranked at \inred{16th} popular web site accroding
to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.

When the given arguments of a function invokation are concrete values, we can
perform dynamic analysis instead of static analysis. For example, The
\jscode{changeCountry} function is invoked when a country different with the
current one is selected in registration of Zoom meetings.  When the ``United
States of America'' (USA) is selected, it calls the \jscode{concat} function
with two pre-defined concrete values as arguments to load USA state information
in line 17-18.  The first argument is an array literal \jscode{[["Other",
"Other"]]} and the second one is an array of pairs of abbreviations and names of
USA states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
\jscode{concat} funciton with \jscode{\_} as \jscode{this} value and above two
concrete values as arguments.  It increases performance of static analysis by
skipping the analysis of function call in line 17-18 and utilizing the result of
dynamic analysis.

Dynamic analysis is still applicable using sealed symbolic concrete execution even if the
arguments are not concrete values.  The \jscode{getData} function is another
part to use \jscode{concat} function but we can only partially apply dynamic
analysis in this case.  It is invoked when loading more Zoom events in
``Webinars \& Events'' page.  At the first time, initial eight events are stored
in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
\jscode{getData} sends a POST request to the server and receives additional
event information \jscode{e} in line 24.  Then, eight events in
\jscode{e.events} are appended to \jscode{this.pastEvents} using the
\jscode{concat} function in line 27-28.  In this case, arguments are not
deterministic but dependent on the given data from the server.  However, we know
that the number of arguments are still deterministically defined as \jscode{2}
and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
because it just checks the length of \jscode{arguments} and passes its elements
to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
able to be evaluated using concrete semantics because we know that \code{array}
is an abstract array.  Only copying via \jscode{copyArray}, flattening via
\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
semantics.  This is the core idea of sealed symbolic execution to maximize the
part of dynamic analysis during static analysis.

>>>>

The functions in Lodash are popular to implement common functionalities for
websites as well.
We excerpt two functions \jscode{changeCountry} in Figure~\ref{fig:changeCountry}
and \jscode{getData} in Figure~\ref{fig:getData} from the \code{zoom.us}~\cite{zoom} site.
The website \code{zoom.us} is ranked at \inred{16th} popular web site accroding
to Alexa~\footnote{https://www.alexa.com/siteinfo/zoom.us} in November 2020.
The \jscode{changeCountry} is the example of using \jscode{concat} only with
concrete values.
The \jscode{changeCountry} function is invoked when a user selects his/her
country on the dropdown list in the register page.
When the user selects ``United States of America'', \jscode{changeCountry} calls
the \jscode{concat} function in line 17-18 to prepare the array for
``State/Province'' dropdown list.
The first argument of \jscode{concat} is an array literal \jscode{[["Other",
"Other"]]} and the second one is an array of pairs of abbreviations and names of
the states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Thus, \jscode{changeCountry} always invokes \jscode{concat} with concrete values.
In the case of \jscode{getData}, \jscode{concat} works with unknown values.
The \jscode{getData} function is invoked when loading more Zoom events in
``Webinars \& Events'' page.
At the first time, initial eight events appear on the page.
For each click of the ``Load More'' button, the \jscode{getData} sends a POST
request to the server and receives data of 8 more events by calling \jscode{concat} in line 28.
As a result, the events list on the page keeps growing by 8.
Both functions, selecting an option of dropdown list and loading more contents
from server-side, are familiar to users.

Existing techniques: static analysis, dynamic analysis, and combined analysis
have limitations to deal with the program containing \jscode{changeCountry} and
\jscode{getData}.
Static analyses of low degrees of context sensitivity tend to cause the
precision loss during analyzing \jscode{concat} function.
The loop in line 7-8 can lead to messing up every property value of args object.
Moreover, \jscode{baseFlatten} has a recursive call that is another challenge
for static analysis.
High degrees of context sensitivity is the promising way, but its computaion
cost is the burden.
Dynamic analyses can show much higher performance for the \jscode{concat} call
by \jscode{changeCountry} than static analyses without any unsoundness and
precision loss.
However, they cannot cover all possible behavior of the \jscode{concat} call
by \jscode{getData} originated by unknown server-side data.
A promising form of combined analysis is dynamically analyzing the call by \jscode{changeCountry}
and statically analyzing the call by \jscode{getData} that is not possible by
existing combined analyses.
User events trigger both functions, the order of function calls is
non-deterministic, so the proper point to divide stages for combined analyses
does not exist.
The syntactic division of the program imposes to choose only one kind of analysis
for the \jscode{concat} function that restricts the benefits of combined analysis.

We present a more flexible and fine-grained method to combine two analyses to
maximize the benefits.

Our observation is

%When the given arguments of a function invokation are concrete values, we can
%perform dynamic analysis instead of static analysis. For example, The
%\jscode{changeCountry} function is invoked when a country different with the
%current one is selected in registration of Zoom meetings.  When the ``United
%States of America'' (USA) is selected, it calls the \jscode{concat} function
%with two pre-defined concrete values as arguments to load USA state information
%in line 17-18.  The first argument is an array literal \jscode{[["Other",
%"Other"]]} and the second one is an array of pairs of abbreviations and names of
%USA states defined as follows:
%\begin{lstlisting}[style=myJSstyle,numbers=none]
%WebinarBase.questions.state.items =
%  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
%\end{lstlisting}
%Moreover, \jscode{this} value is also a concrete value, the Lodash top-level
%object \jscode{\_}.  Thus, we could perform dynamic analysis by invoking the
%\jscode{concat} funciton with \jscode{\_} as \jscode{this} value and above two
%concrete values as arguments.  It increases performance of static analysis by
%skipping the analysis of function call in line 17-18 and utilizing the result of
%dynamic analysis.
%
%Dynamic analysis is still applicable using lazy concrete execution even if the
%arguments are not concrete values.  The \jscode{getData} function is another
%part to use \jscode{concat} function but we can only partially apply dynamic
%analysis in this case.  It is invoked when loading more Zoom events in
%``Webinars \& Events'' page.  At the first time, initial eight events are stored
%in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
%\jscode{getData} sends a POST request to the server and receives additional
%event information \jscode{e} in line 24.  Then, eight events in
%\jscode{e.events} are appended to \jscode{this.pastEvents} using the
%\jscode{concat} function in line 27-28.  In this case, arguments are not
%deterministic but dependent on the given data from the server.  However, we know
%that the number of arguments are still deterministically defined as \jscode{2}
%and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
%with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
%dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
%because it just checks the length of \jscode{arguments} and passes its elements
%to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
%able to be evaluated using concrete semantics because we know that \code{array}
%is an abstract array.  Only copying via \jscode{copyArray}, flattening via
%\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
%semantics.  This is the core idea of lazy concrete execution to maximize the
%part of dynamic analysis during static analysis.
